\input{myassignmentpreamble}
\input{ciss430}
\input{yliow}
\renewcommand\TITLE{Assignment 6}

\begin{document}
\topmatter

\textsc{Objectives}
\begin{enumerate}
\item Write queries using relational algebra operators.
\end{enumerate}

\newcommand\stringtype{\texttt{string}}
\newcommand\integertype{\texttt{integer}}
\newcommand\realtype{\texttt{real}}

\newcommand\Suppliers{\texttt{Suppliers}}
\newcommand\Parts{\texttt{Parts}}
\newcommand\Catalog{\texttt{Catalog}}
\newcommand\sid{\texttt{sid}}
\newcommand\sname{\texttt{sname}}
\newcommand\pid{\texttt{pid}}
\newcommand\pname{\texttt{pname}}
\newcommand\mycolor{\texttt{color}}
\newcommand\cost{\texttt{cost}}
\newcommand\address{\texttt{address}}

Enter your answers in \verb!q1.tex!, \verb!q2.tex!, etc.

Hans Solo need to get some parts to fix the Millenium Falcon.
Unfortunately the website is down.
You'll have to help him enter the queries using relational algebra.

Here's the schemas of the database at the rebel base:

\begin{console}[commandchars=\\\{\},frame=none,fontsize=\normalsize]
    \Suppliers(\sid: \integertype, \sname: \stringtype, \address: \stringtype)
    \Parts(\pid: \integertype, \pname: \stringtype, \mycolor: \stringtype)
    \Catalog(\sid: \integertype, \pid: \integertype, \cost: \realtype)
\end{console}

(Note: There are \LaTeX\ macros for the
relations and the column names.
See \verb!main.tex!.
For instance \verb!\Suppliers! gives you \Suppliers.

Set operations:
\[
 \cup  \hspace{1cm}
 \cap  \hspace{1cm}
 - 
\]
Relational algebra operators:
\[
\sigma \hspace{1cm}
\pi    \hspace{1cm}
\rho
\]
Comparison:
\[
=     \hspace{1cm}
\neq  \hspace{1cm}
<     \hspace{1cm}
\leq  \hspace{1cm}
>     \hspace{1cm}
\geq
\]

Logical operators:
\[
\lnot   \hspace{1cm}   \land   \hspace{1cm}   \lor
\]

Cross product and join:
\[
\times   \hspace{1cm}
\Join_{a = b}
\]

Example:
\[
\sigma_{\sid = 42}(\Suppliers)
\]
\[
\sigma_{\sid \neq 42}(\Suppliers)
\]
\[
\sigma_{\lnot (\sid < 42)}(\Suppliers)
\]
\[
\sigma_{\sid \leq 42 \land \sname = \texttt{'Bar'} }(\Suppliers)
\]
\[
\rho(T(\sid \rightarrow a), \Suppliers)
\]

%------------------------------------------------------------------------------
\newpage
Q1.
Find the names of suppliers who supply some red part.

\SOLUTION
\input{q1.tex}

%------------------------------------------------------------------------------
\newpage
Q2.
Find the sids of suppliers who supply some red or green part.

\SOLUTION
\input{q2.tex}

%------------------------------------------------------------------------------
\newpage
Q3.
Find the sids of suppliers who supply some red part or are at 221 Baker Street.

\SOLUTION
\input{q3.tex}

%------------------------------------------------------------------------------
\newpage
Q4.
Find the sids of suppliers who supply some red part and some green part.

\SOLUTION
\input{q4.tex}

%------------------------------------------------------------------------------
\newpage
Q5.
Find the sids of suppliers who supply every part.

\SOLUTION
\input{q5.tex}

%------------------------------------------------------------------------------
\newpage
Q6.
Find the sids of suppliers who supply every red part.

\SOLUTION
\input{q6.tex}

%------------------------------------------------------------------------------
\newpage
Q7.
Find the sids of suppliers who supply every red or green part.

\SOLUTION
\input{q7.tex}

%------------------------------------------------------------------------------
\newpage
Q8.
Find the sids of suppliers who supply every red part or supply every green part.

\SOLUTION
\input{q8.tex}

%------------------------------------------------------------------------------
\newpage
Q9.
Find pairs of sids such that the supplier with the first
sid charges more for some part than the supplier with the second sid.

\SOLUTION
\input{q9.tex}

%------------------------------------------------------------------------------
\newpage
Q10.
Find the pids of parts supplied by at least two different suppliers.

\SOLUTION
\input{q10.tex}

%------------------------------------------------------------------------------
\newpage
Q11.
Find the pids of the most expensive parts supplied by suppliers
names Jabba the Hutt.

\SOLUTION
\input{q11.tex}

%------------------------------------------------------------------------------
\newpage
Q12.
Find the pids of parts supplied by every supplier at less than \$200.
(If any supplier either does not supply the part
or
charges more than \$200 for it, the part is not selected.)

\SOLUTION
\input{q12.tex}

%------------------------------------------------------------------------------
\end{document}
