\input{thispreamble.tex}

\input{preamble-instructions.tex}

\begin{center}
  \textsc{Honor Statement}
\end{center}
I, \answerbox{[Nathan Cochran]},
attest to the fact that the submitted work is my own and
is not the result of plagiarism.
Furthermore, I have not aided another student in the act of
plagiarism.

\input{preamble.tex}

\newpage
Q1. \input{q1.tex}

\textsc{Answer}
\begin{answercode}
SELECT eid FROM Certified WHERE
aid = (SELECT aid FROM Aircraft WHERE aname = 'Flight Crew Shuttle');
\end{answercode}




Q2. \input{q2.tex}

\textsc{Answer}
\begin{answercode}
SELECT ename FROM Employee WHERE
eid = (SELECT eid FROM Certified WHERE
    aid = (SELECT aid FROM Aircraft WHERE
           aname = 'Flight Crew Shuttle')
       AND Certified.eid = Employee.eid);
\end{answercode}


\newpage
Q3. \input{q3.tex}

\textsc{Answer}
\begin{answercode}
Note: Beggar's Canyon is written as Beggars Canyon

SELECT aid FROM Aircraft WHERE
cruisingrange >= (SELECT distance FROM Flights WHERE
from_ = 'Beggars Canyon' AND to_ = 'Dune Sea Exchange');
\end{answercode}


Q4. \input{q4.tex}

\textsc{Answer}
\begin{answercode}
SELECT aid FROM Aircraft WHERE
(SELECT COUNT(Certified.aid) FROM Certified WHERE
Certified.aid = Aircraft.aid AND eid =
(SELECT eid FROM Employee WHERE Certified.eid = Employee.eid
AND salary > 100)) = (SELECT COUNT(eid) FROM Employee
WHERE salary > 100);
\end{answercode}


\newpage

Q5. \input{q5.tex}

\textsc{Answer}
\begin{answercode}
SELECT ename FROM Employee WHERE (SELECT COUNT(eid) FROM Certified WHERE
aid = (SELECT aid FROM Aircraft WHERE Aircraft.aid = Certified.aid
AND cruisingrange > 2000) > 0 AND Certified.eid = Employee.eid)
AND
(SELECT COUNT(aid) FROM Certified WHERE
Certified.eid = Employee.eid AND
Certified.aid = (SELECT aid FROM Aircraft WHERE
aname = 'Flight Crew Shuttle')) < 1;
\end{answercode}


Q6. \input{q6.tex}

\textsc{Answer}
\begin{answercode}
SELECT eid FROM Employee WHERE salary = (SELECT Max(salary)
FROM Employee);
\end{answercode}


\newpage

Q7. \input{q7.tex}

\textsc{Answer}
\begin{answercode}
SELECT eid FROM Employee WHERE salary = (SELECT Max(salary)
FROM Employee WHERE salary < (SELECT Max(salary) from Employee));
\end{answercode}




Q8. \input{q8.tex}

\textsc{Answer}
\begin{answercode}
ERROR
I believe this question is impossible to answer because answering this
would require generating a temporary table of the # of certifications
each employee has, which requires a loop. Unfortunately, there is no
concept of a loop in SQL, so which would require programmatic access
to loop over Employee, generate a temporary table of maxes, and then
perform the following SQL query, where maxtable is a temporary table.

SELECT eid FROM Employee WHERE (SELECT COUNT(aid) FROM Certified
WHERE Employee.eid = Certified.eid) = (SELECT MAX(max) FROM maxtable);
\end{answercode}


\newpage
Q9. \input{q9.tex}

\textsc{Answer}
\begin{answercode}
SELECT eid FROM Employee WHERE (SELECT COUNT(aid) FROM
Certified WHERE Employee.eid = Certified.eid) = 3;
\end{answercode}




Q10. \input{q10.tex}

\textsc{Answer}
\begin{answercode}
SELECT SUM(salary) FROM Employee;
\end{answercode}


\newpage
Q11. \input{q11.tex}

\textsc{Answer}
\begin{answercode}
Note: This problem is likely impossible, depending on the complexity
of the map layout. However, if we assume that every location can
have one and only one connection from it, then the following
recursive query will determine if any path exists. If not, it return
an empty query. If it does, it will return the # of steps required
to get to the destination.

Note: I use to_ and from_ instead of to and from for the Flights
table schema.

WITH RECURSIVE T(f, t, step, path_found)
AS (
	 SELECT ('Raider Camp'), (SELECT to_ FROM Flights WHERE
          from_ = 'Raider Camp'), 1, 'FALSE'
	 UNION ALL
	 SELECT t,
   (SELECT to_ FROM Flights WHERE from_ = t),
   step+1,
   (CASE WHEN ((SELECT to_ FROM Flights WHERE
   from_ = t) = 'Rebel Depot') THEN 'TRUE' ELSE 'FALSE' END)
   FROM T WHERE step < 10 AND (SELECT COUNT(to_)
   FROM Flights WHERE from_ = t) > 0
) SELECT step AS steps_to_take from T WHERE path_found = 'TRUE';
\end{answercode}




\newpage
\input{supportticket.tex}


\newpage
\input{q12.tex}

\textsc{Answer}
\begin{answercode}
CREATE TABLE SupportTickets (
			 sid INT AUTO_INCREMENT PRIMARY KEY,
			 email VARCHAR(200),
			 subject VARCHAR(200)
);

CREATE TABLE Employees (
			 eid INT PRIMARY KEY,
			 name VARCHAR(200)
);

CREATE TABLE Notes (
			 nid INT AUTO_INCREMENT PRIMARY KEY,
			 sid INT,
			 eid INT,
			 state INT,
			 note VARCHAR(200),
			 time INT
);
\end{answercode}




\newpage
\input{q13.tex}

\textsc{Answer}
\begin{answercode}
INSERT INTO SupportTickets (email, subject) VALUES
('test_email@gmail.com', 'Question #1'),
('test2_email@gmail.com', 'Question #2'),
('test3_email@gmail.com', 'Question #3');

INSERT INTO Employees (eid, name) VALUES
(3, 'John Doe'),
(97, 'Blake Deere');


INSERT INTO Notes (sid, eid, state, note, time) VALUES
(
  (SELECT sid FROM SupportTickets WHERE subject = 'Question #1'),
  (SELECT eid FROM Employees WHERE name = 'John Doe'),
  0,
  'Hey I have a problem X!',
  5
),
(
  (SELECT sid FROM SupportTickets WHERE subject = 'Question #1'),
  (SELECT eid FROM Employees WHERE name = 'John Doe'),
  0,
  'Hurry Up!!!',
  6
),
(
  (SELECT sid FROM SupportTickets WHERE subject = 'Question #1'),
  (SELECT eid FROM Employees WHERE name = 'Blake Deere'),
  9,
  'Here is the solution for X!',
  10
),
(
  (SELECT sid FROM SupportTickets WHERE subject = 'Question #1'),
  (SELECT eid FROM Employees WHERE name = 'John Doe'),
  0,
  'That did not completely fix problem X!',
  24
),
(
  (SELECT sid FROM SupportTickets WHERE subject = 'Question #1'),
  (SELECT eid FROM Employees WHERE name = 'Blake Deere'),
  9,
  'Try this other thing to fix X!',
  30
),
(
  (SELECT sid FROM SupportTickets WHERE subject = 'Question #1'),
  (SELECT eid FROM Employees WHERE name = 'John Doe'),
  0,
  'That still does not fix it!',
  45
),
(
  (SELECT sid FROM SupportTickets WHERE subject = 'Question #1'),
  (SELECT eid FROM Employees WHERE name = 'Blake Deere'),
  9,
  'Our apologies, try this last final solution!',
  68
);
\end{answercode}


\newpage
Q12. \input{q14.tex}

\textsc{Answer}
\begin{answercode}
CREATE TEMPORARY TABLE T1 AS
SELECT N1.sid, N1.note AS N1_note, N1.time AS N1_time, N2.note AS
N2_note, N2.time AS N2_time, N2.time - N1.time AS wait
FROM Notes AS N1
JOIN
Notes AS N2
ON N1.sid = N2.sid
WHERE N1.state = 0
AND N2.state = 9
AND N2.time > N1.time
AND N2.time = (SELECT MIN(N3.time) FROM Notes AS
N3 WHERE N3.time > N1.time AND N3.state = 9);

SELECT * FROM T1;
SELECT SUM(wait) FROM T1;
\end{answercode}

\end{document}
